Non-Vertical Cultural Transmission, Assortment, \\and the Evolution of Cooperation

### 2020-09-24 ms/main.tex
reorder conditions in result 3

% in gamma
\begin{enumerate}
\item \emph{Fixation of cooperation}: 
	if \emph{(i)} $T_A \ge T_B$ and $c < \hat\gamma_1$; or 
	if \emph{(ii)} $T_A < T_B$ and $v>\hat v$ and $c < \hat\gamma_2$.
\item \emph{Fixation of defection}: 
    if \emph{(iii)} $T_A \ge T_B$ and $\hat\gamma_2 < c$; or 
	if \emph{(iv)} $T_A < T_B$ and $\hat\gamma_1 < c$.
\item \emph{Stable Coexistence}: 
    if \emph{(v)} $T_A < T_B$ and $v>\hat{v}$ and $\hat\gamma_2 < c < \hat\gamma_1$; or
    if \emph{(vi)} $T_A < T_B$ and $v<\hat{v}$ and $c < \hat\gamma_1$.
\item \emph{Unstable coexistence}:
    if \emph{(vii)} $T_A > T_B$ and $\hat\gamma_1 < c < \hat\gamma_2$.
\end{enumerate}

>>>>

% in gamma
\begin{enumerate}
\item \emph{Fixation of cooperation}: 
	if \emph{(i)} $T_A \ge T_B$ and $c < \hat\gamma_1$; or 
	if \emph{(ii)} $T_A < T_B$ and $v>\hat v$ and $c < \hat\gamma_2$.
\item \emph{Fixation of defection}: 
    if \emph{(iii)} $T_A \ge T_B$ and $\hat\gamma_2 < c$; or 
	if \emph{(iv)} $T_A < T_B$ and $\hat\gamma_1 < c$.
\item \emph{Stable Coexistence}: 
    if \emph{(v)} $T_A < T_B$ and $v<\hat{v}$ and $c < \hat\gamma_1$; or 
    if \emph{(vi)} $T_A < T_B$ and $v>\hat{v}$ and $\hat\gamma_2 < c < \hat\gamma_1$.
\item \emph{Unstable coexistence}:
    if \emph{(vii)} $T_A > T_B$ and $\hat\gamma_1 < c < \hat\gamma_2$.
\end{enumerate}
